---
output:
  html_document: default
  pdf_document: default
---

```{r define_course, include=FALSE, message=FALSE, warning=FALSE}
# run these lines to save the google token before knitting this 
# token <- gs_auth(new_user=T)
# saveRDS(token, file = 'googlesheets_token.rds')
token <- 'googlesheets_token.rds'

whichTraining <- "CRRL, Cook, WA (11/01/2016 thru 11/03/2016)"
isPre <- FALSE
isPost <- TRUE
isInstructorReport <- TRUE
isProjectTime <- TRUE
```

# Course Feedback Summary
##### `r format(Sys.time(), "%b %d, %Y") `
##### `r whichTraining `

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(googlesheets)
library(dplyr)
library(ggplot2)
library(knitr)
library(pander)
library(htmlTable)

opts_chunk$set(echo=FALSE,message=FALSE, warning=FALSE)

cat("\n\n")
```

##### Table of Contents 

```{r results='asis', eval=isPre} 
cat("- [How much experience do you have in R?](#pre_experience)")
cat("\n")

if(isInstructorReport){
  cat("- [Which of these skills do you want us to emphasize during the workshop?](#pre_skillemphasis)")
  cat("\n")
  cat("- [How long would it take you to do the following in R?](#pre_timepertopic)")
  cat("\n")
}

cat("- [For me, this workshop would be a success if . . .](#pre_successif)")
cat("\n")
```

```{r results='asis', eval=isPost} 

cat("- [Overall, how satisfied were you with the R training course you recently attended?](#post_overall)")
cat("\n")
cat("- [How likely would you be to recommend this course to others?](#post_recommend)")
cat("\n")
cat("- [How appropriate was the 2.5 day length of the workshop?](#post_length)")
cat("\n")
cat("- [Was the material taught at a good pace?](#post_pace)")
cat("\n")
cat("- [Was there enough one-on-one interaction between students and instructor, given the class size?](#post_interaction)")
cat("\n")

if(isInstructorReport){
  cat("- [What did you think about the time spent on each of the topics?](#post_timepertopic)")
  cat("\n")
  cat("- [What topics were NOT covered in the course that, if included, would increase the usefulness of the course to you?](#post_notcovered)")
  cat("\n")
}

if(isProjectTime){
  cat("- [How useful was the project time?](#post_projectuseful)")
  cat("\n")
  cat("- [What did you gain from the project time?](#post_projectgain)")
  cat("\n")
}

cat("- [Is there any additional feedback you would like the instructors of the course to receive?](#post_comments)")
cat("\n")
```

```{r get_current_feedback, echo=FALSE, message=FALSE}
gs_auth(token)

# list sheets found
sheet_found <- gs_ls()

#\\#\\# pre-assessment #\\#\\#
if(isPre){
  # register the spreadsheet by title (must occur in order to read it in)
  sheet_registered_pre <- gs_title("R Pre-Workshop Assessment (Responses)")
  
  # read in the data
  preData <- gs_read(sheet_registered_pre)
  
  #fix invalid characters (square brackets) in column names
  valid_column_names <- make.names(names=names(preData), unique=TRUE, allow_ = TRUE)
  names(preData) <- valid_column_names
  
  course_feedback_pre <- preData %>% 
    filter(Which.training.will.you.be.attending. == whichTraining)
}

#\\#\\# post-assessment #\\#\\#
if(isPost){
  # register the spreadsheet by title (must occur in order to read it in)
  sheet_registered_post <- gs_title("R Post-Workshop Assessment (Responses)")
  # read in the data
  postData <- gs_read(sheet_registered_post)
  
  course_feedback_post <- postData %>% 
    filter(`Which training did you attend?` == whichTraining) %>%
    #get these columns just as numbers.
    mutate_at(., 
              vars(contains("What did you think about the time spent on each of the topics?")), 
              gsub,
              pattern = '[^0-9]', replacement="") 
  
}
```


```{r plot_setup, echo=FALSE}

table_comments <- function(df, colName){
  whichCol <- which(names(df) == colName)
  comments <- df[,whichCol]
  comments <- comments[!is.na(comments[,1]),1]
  colnames(comments) <- NULL
  return(comments)
}

bar_results <- function(df, colName, lowValLabel=NULL, highValLabel=NULL, 
                        levels=NULL, labels=NULL, plot_title=""){
  # levels for post-workshop answers are 1-5, but pre-workshop needs special levels defined
  if(is.null(levels)){
    levels <- 1:5
  }
  
  if(is.null(labels)){
    labels <- levels
  }
  
  sepchar <- ifelse(!is.null(lowValLabel), " >> ", "")
  
  whichCol <- which(names(df) == colName)
  df[whichCol] <- factor(x = df[[whichCol]], levels = levels, labels = labels, ordered = TRUE)

  bar_results_plot <- ggplot(data = df, aes(x = df[[whichCol]])) +
    xlab(paste(lowValLabel, highValLabel, sep=sepchar)) + 
    geom_bar(color = "goldenrod1", fill = "goldenrod1") +
    ggtitle(plot_title)
  
  print(bar_results_plot)
}
```

## `r if(isPre){ "Pre-workshop Feedback" }`

#### `r if(isPre){ "How much experience do you have in R?" }`

```{r pre_experience, echo=FALSE, eval=isPre, fig.height=4, fig.width=8}
pie_data <- table(course_feedback_pre$How.much.experience.do.you.have.in.R.)
lbls <- paste(names(pie_data), "\n", pie_data, sep="")
pie(pie_data, labels = lbls, border = NA, col = c('dodgerblue2', 'firebrick2', 
                                     'goldenrod1', 'forestgreen'))
```

#### `r if(isPre && isInstructorReport){ "Which of these skills do you want us to emphasize during the workshop?" }`

```{r pre_skillemphasis, echo=FALSE, eval=isPre&&isInstructorReport, fig.height=4, fig.width=8}
whattoemphasize_levels <- c('Cover the basics', 'Cover the advanced stuff', 
                      'Cover it all', "Don't bother (I know it already)", 
                      "Don't bother (not important to me)")

whattoemphasize_col <- "Which.of.these.skills.do.you.want.us.to.emphasize.during.the.workshop..."
whattoemphasize_colnames <- names(course_feedback_pre)[grepl(whattoemphasize_col, names(course_feedback_pre))]
whattoemphasize_titles <- gsub(pattern="\\.", replacement=" ", 
                               gsub(pattern="\\.\\.", replacement=", ", 
                                    gsub(pattern=whattoemphasize_col, replacement="",
                                         whattoemphasize_colnames)))
whattoemphasize_vars <- data.frame(colname = whattoemphasize_colnames, title = whattoemphasize_titles)

invisible(apply(whattoemphasize_vars, MARGIN=1, 
                FUN = function(w, df, levels){
                  bar_results(df, colName=w['colname'], levels=levels, plot_title=w['title'])
                }, 
                df = course_feedback_pre, 
                levels = whattoemphasize_levels))
```

#### `r if(isPre && isInstructorReport){ "How long would it take you to do the following in R?" }`

```{r pre_timepertopic, echo=FALSE, eval=isPre&&isInstructorReport, fig.height=4, fig.width=8}
timeittakes_levels <- c("Forever (phone a friend)", "3 hours (with the internet)", 
                     "30 minutes (trial & error)", "5 minutes (easy)")

timeittakes_col <- "How.long.would.it.take.you.to.do.the.following.in.R..."
timeittakes_colnames <- names(course_feedback_pre)[grepl(timeittakes_col, names(course_feedback_pre))]
timeittakes_titles <- gsub(pattern="\\.", replacement=" ", 
                           gsub(pattern="\\.\\.", replacement=", ",
                                gsub(pattern=timeittakes_col, replacement="", 
                                     timeittakes_colnames)))
timeittakes_vars <- data.frame(colname = timeittakes_colnames, title = timeittakes_titles)

invisible(apply(timeittakes_vars, MARGIN=1,
                FUN = function(t, df, levels){
                   bar_results(df, colName=t['colname'], levels=levels, plot_title=t['title'])
                 }, 
                df = course_feedback_pre, 
                levels = timeittakes_levels))
```

#### `r if(isPre){ "For me, this workshop would be a success if . . ." }`

```{r pre_successif, echo=FALSE, eval=isPre}
comments_pre <- table_comments(df = course_feedback_pre, 
                               colName = "For.me..this.workshop.would.be.a.success.if......")

htmlTable(comments_pre, align = 'l', col.rgroup = c("none", "#E0E0E0"))
```

## `r if(isPost){ "Post-workshop Feedback" }`

#### `r if(isPost){ "Overall, how satisfied were you with the R training course you recently attended?" } `

```{r post_overall, echo=FALSE, eval=isPost, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "Overall, how satisfied were you with the R training course you recently attended?",
            lowValLabel = "Not satisfied", highValLabel = "Very satisfied")
```

#### `r if(isPost){ "How likely would you be to recommend this course to others?" } `

```{r post_recommend, echo=FALSE, eval=isPost, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "How likely would you be to recommend this course to others?",
            lowValLabel = "Not likely", highValLabel = "Very likely")
```

#### `r if(isPost){ "How appropriate was the 2.5 day length of the workshop?" } `

```{r post_length, echo=FALSE, eval=isPost, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "How appropriate was the 2.5 day length of the workshop? (3=great)",
            lowValLabel = "Too short", highValLabel = "Too long")
```

#### `r if(isPost){ "Was the material taught at a good pace?" } `

```{r post_pace, echo=FALSE, eval=isPost, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "Was the material taught at a good pace? (3=great)",
            lowValLabel = "Too slow", highValLabel = "Too fast")
```

#### `r if(isPost){ "Was there enough one-on-one interaction between students and instructor, given the class size?" } `

```{r post_interaction, echo=FALSE, eval=isPost, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "Was there enough one-on-one interaction between students and instructor, given the class size?",
            lowValLabel = "Enough", highValLabel = "Not enough")
```


#### `r if(isPost && isInstructorReport){ "What did you think about the time spent on each of the topics?" }`

```{r post_timepertopic, echo=FALSE, eval=isPost&&isInstructorReport, fig.height=4, fig.width=8}
timepertopic_labels <- c("Way too little time", "Too little time", "Just the right amount of time", 
                         "Too much time", "Way too much time")

timepertopic_col <- "What did you think about the time spent on each of the topics?"
timepertopic_colnames <- names(course_feedback_post)[grepl(timepertopic_col, names(course_feedback_post))]
timepertopic_titles <- gsub(pattern="]", replacement="", 
                           gsub(pattern=".+\\[", replacement="", 
                                timepertopic_colnames))
timepertopic_vars <- data.frame(colname = timepertopic_colnames, title = timepertopic_titles)

invisible(apply(timepertopic_vars, MARGIN=1,
                FUN = function(t, df, lowValLabel, highValLabel, labels){
                   bar_results(df, colName=t['colname'], lowValLabel, highValLabel, 
                               labels = labels, plot_title=t['title'])
                 }, 
                df = course_feedback_post,
                lowValLabel = "Not enough time", highValLabel = "Too much time",
                labels = timepertopic_labels))
```

##### `r if(isPost && isInstructorReport){ "What topics were NOT covered in the course that, if included, would increase the usefulness of the course to you?" }`

```{r post_notcovered, echo=FALSE, eval=isPost&&isProjectTime}
comments_post <- table_comments(df = course_feedback_post, 
                                colName = "What topics were NOT covered in the course that, if included, would increase the usefulness of the course to you?")
htmlTable(comments_post, align = 'l', col.rgroup = c("none", "#E0E0E0"))
```

#### `r if(isPost && isProjectTime){ "How useful was the project time?" }`

```{r post_projectuseful, echo=FALSE, eval=isPost&&isProjectTime, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "How useful was the project time?",
            lowValLabel = "Not useful", highValLabel = "Very useful")
```

#### `r if(isPost && isProjectTime){ "What did you gain from the project time?" }`

```{r post_projectgain, echo=FALSE, eval=isPost&&isProjectTime}
comments_post <- table_comments(df = course_feedback_post, 
                                colName = "What did you gain from the project time?")
htmlTable(comments_post, align = 'l', col.rgroup = c("none", "#E0E0E0"))
```

#### `r if(isPost){ "Is there any additional feedback you would like the instructors of the course to receive?" }`

```{r post_comments, echo=FALSE, eval=isPost}
comments_post <- table_comments(df = course_feedback_post, 
                                colName = "Is there any additional feedback you would like the instructors of the course to receive? If so, please share below.")
htmlTable(comments_post, align = 'l', col.rgroup = c("none", "#E0E0E0"))
```
