---
title: "Course Feedback Summary"
author: "Lindsay R. Carr"
date: "May 9, 2016"
output: html_document
subtitle: Ft. Collins, CO (04/26/2016 thru 04/28/2016)
---

```{r setup, include=FALSE}
whichTraining <- "Ft. Collins, CO (04/26/2016 thru 04/28/2016)"

library(googlesheets)
library(dplyr)
library(ggplot2)
library(knitr)
library(pander)
library(htmlTable)
```


```{r get_current_feedback, echo=FALSE, message=FALSE}
# browser will open requiring you to authenticate (first time you run this)
sheet_found <- gs_ls()

#\\#\\# pre-assessment #\\#\\#

# register the spreadsheet by title (must occur in order to read it in)
sheet_registered_pre <- gs_title("R Pre-Workshop Assessment (Responses)")
# read in the data
course_feedback_pre_all <- gs_read(sheet_registered_pre)

##fix invalid characters (square brackets) in column names
valid_column_names <- make.names(names=names(course_feedback_pre_all), unique=TRUE, allow_ = TRUE)
names(course_feedback_pre_all) <- valid_column_names

course_feedback_pre <- course_feedback_pre_all %>% 
  filter(Which.training.will.you.be.attending. == whichTraining)

#\\#\\# post-assessment #\\#\\#

# register the spreadsheet by title (must occur in order to read it in)
sheet_registered_post <- gs_title("R Post-Workshop Assessment (Responses)")
# read in the data
course_feedback_post_all <- gs_read(sheet_registered_post)

course_feedback_post <- course_feedback_post_all %>% 
  filter(`Which training did you attend?` == whichTraining)
```


```{r plot_setup, echo=FALSE}

table_comments <- function(df, colName){
  whichCol <- which(names(df) == colName)
  comments <- df[,whichCol]
  comments <- comments[!is.na(comments[,1]),1]
  colnames(comments) <- NULL
  return(comments)
}

bar_results <- function(df, colName){
  whichCol <- which(names(df) == colName)
  df[whichCol] <- factor(x = df[[whichCol]], levels = 1:5, ordered = TRUE)

  ggplot(data = df, aes(x = df[[whichCol]])) +
    xlab("") + 
    geom_bar(color = "goldenrod1", fill = "goldenrod1")
}
```

# Pre-workshop Feedback

### How much experience do you have in R?

```{r echo=FALSE}
pie_data <- table(course_feedback_pre$How.much.experience.do.you.have.in.R.)
lbls <- paste(names(pie_data), "\n", pie_data, sep="")
pie(pie_data, labels = lbls, border = NA, col = c('dodgerblue2', 'firebrick2', 
                                     'goldenrod1', 'forestgreen'))
```

### For me, this workshop would be a success if . . .

```{r echo=FALSE}
comments_pre <- table_comments(df = course_feedback_pre, 
                               colName = "For.me..this.workshop.would.be.a.success.if......")

htmlTable(comments_pre, align = 'l', col.rgroup = c("none", "#E0E0E0"))
```

# Post-workshop feedback

### Overall, how satisfied were you with the R training course you recently attended?

```{r echo=FALSE, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "Overall, how satisfied were you with the R training course you recently attended?")
```

### How likely would you be to recommend this course to others?

```{r echo=FALSE, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "How likely would you be to recommend this course to others?")
```

### How appropriate was the 2.5 day length of the workshop? (3=great)

```{r echo=FALSE, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "How appropriate was the 2.5 day length of the workshop? (3=great)")
```

### Was the material taught at a good pace? (3=great)

```{r echo=FALSE, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "Was the material taught at a good pace? (3=great)")
```

### Was there enough one-on-one interaction between students and instructor, given the class size?

```{r echo=FALSE, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "Was there enough one-on-one interaction between students and instructor, given the class size?")
```

### Is there any additional feedback you would like the instructors of the course to receive?

```{r echo=FALSE}
comments_post <- table_comments(df = course_feedback_post, 
                                colName = "Is there any additional feedback you would like the instructors of the course to receive? If so, please share below.")
htmlTable(comments_post, align = 'l', col.rgroup = c("none", "#E0E0E0"))
```




