# Course Feedback Summary
##### `r format(Sys.time(), "%b %d, %Y") `
##### `r whichTraining `

```{r setup, include=FALSE}
library(googlesheets)
library(dplyr)
library(ggplot2)
library(knitr)
library(pander)
library(htmlTable)
```


```{r get_current_feedback, echo=FALSE, message=FALSE}
#\\#\\# pre-assessment #\\#\\#

##fix invalid characters (square brackets) in column names
valid_column_names <- make.names(names=names(preData), unique=TRUE, allow_ = TRUE)
names(preData) <- valid_column_names

course_feedback_pre <- preData %>% 
  filter(Which.training.will.you.be.attending. == whichTraining)

#\\#\\# post-assessment #\\#\\#

course_feedback_post <- postData %>% 
  filter(`Which training did you attend?` == whichTraining) 
```


```{r plot_setup, echo=FALSE}

table_comments <- function(df, colName){
  whichCol <- which(names(df) == colName)
  comments <- df[,whichCol]
  comments <- comments[!is.na(comments[,1]),1]
  colnames(comments) <- NULL
  return(comments)
}

bar_results <- function(df, colName){
  whichCol <- which(names(df) == colName)
  df[whichCol] <- factor(x = df[[whichCol]], levels = 1:5, ordered = TRUE)

  ggplot(data = df, aes(x = df[[whichCol]])) +
    xlab("") + 
    geom_bar(color = "goldenrod1", fill = "goldenrod1")
}
```

## Pre-workshop Feedback

#### How much experience do you have in R?

```{r echo=FALSE}
pie_data <- table(course_feedback_pre$How.much.experience.do.you.have.in.R.)
lbls <- paste(names(pie_data), "\n", pie_data, sep="")
pie(pie_data, labels = lbls, border = NA, col = c('dodgerblue2', 'firebrick2', 
                                     'goldenrod1', 'forestgreen'))
```

#### For me, this workshop would be a success if . . .

```{r echo=FALSE}
comments_pre <- table_comments(df = course_feedback_pre, 
                               colName = "For.me..this.workshop.would.be.a.success.if......")

htmlTable(comments_pre, align = 'l', col.rgroup = c("none", "#E0E0E0"))
```

## Post-workshop feedback

#### Overall, how satisfied were you with the R training course you recently attended?

```{r echo=FALSE, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "Overall, how satisfied were you with the R training course you recently attended?")
```

#### How likely would you be to recommend this course to others?

```{r echo=FALSE, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "How likely would you be to recommend this course to others?")
```

#### How appropriate was the 2.5 day length of the workshop? (3=great)

```{r echo=FALSE, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "How appropriate was the 2.5 day length of the workshop? (3=great)")
```

#### Was the material taught at a good pace? (3=great)

```{r echo=FALSE, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "Was the material taught at a good pace? (3=great)")
```

#### Was there enough one-on-one interaction between students and instructor, given the class size?

```{r echo=FALSE, fig.height=4, fig.width=8}
bar_results(df = course_feedback_post,
            colName = "Was there enough one-on-one interaction between students and instructor, given the class size?")
```

#### Is there any additional feedback you would like the instructors of the course to receive?

```{r echo=FALSE}
comments_post <- table_comments(df = course_feedback_post, 
                                colName = "Is there any additional feedback you would like the instructors of the course to receive? If so, please share below.")
htmlTable(comments_post, align = 'l', col.rgroup = c("none", "#E0E0E0"))
```




